---
title: "Games As Art"
author: "anonymous"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This RMD File prepares one DataSet for the qualitative analysis, one DataSet for the demographic analysis and one DataSet for the network analysis.
The Input is the RawData.xlsx file in the folder "RawData"
The Outputs are saved in the respective Analysis Folders.


#__Setup: Always Run!__#
```{r}
if(!require(tidyverse)){install.packages('tidyverse')}
library(tidyverse, readxl)

##Set Working DIR so Input&Output is correct
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

##Import Data Set
DataSet <- read_tsv("../RawData/RawData.csv")
```
#__Renaming Columns__#
```{r}
#Array for AESTHEMOS Names:
AESTHEMOS1 <- c("IntellectualChallenge_1_AESTHEMOS","Relaxation_1_AESTHEMOS","FeelingOfBeauty_1_AESTHEMOS","Enchantment_1_AESTHEMOS","IntellectualChallenge_2_AESTHEMOS","FeelingOfUgliness_2_AESTHEMOS","BeingMoved_1_AESTHEMOS","Energy_2_AESTHEMOS","Enchantment_2_AESTHEMOS","Relaxation_2_AESTHEMOS","Humor_1_AESTHEMOS","Confusion_1_AESTHEMOS","Nostalgia_2_AESTHEMOS","Nostalgia_1_AESTHEMOS","Uneasiness_2_AESTHEMOS", "Vitality_1_AESTHEMOS", "Fascination_1_AESTHEMOS", "BeingMoved_2_AESTHEMOS", "Interest_2_AESTHEMOS", "Awe_1_AESTHEMOS", "Humor_2_AESTHEMOS")

AESTHEMOS2 <- c("FeelingOfBeauty_2_AESTHEMOS", "Joy_1_AESTHEMOS", "Interest_1_AESTHEMOS", "Fascination_2_AESTHEMOS", "Vitality_2_AESTHEMOS", "Surprise_1_AESTHEMOS", "Insight_1_AESTHEMOS", "Sadness_1_AESTHEMOS", "Anger_1_AESTHEMOS", "Boredom_1_AESTHEMOS", "Insight_2_AESTHEMOS", "Sadness_2_AESTHEMOS", "Anger_2_AESTHEMOS", "Uneasiness_1_AESTHEMOS", "Surprise_2_AESTHEMOS", "Awe_2_AESTHEMOS", "Boredom_2_AESTHEMOS", "FeelingOfUgliness_1_AESTHEMOS", "Confusion_2_AESTHEMOS", "Joy_2_AESTHEMOS", "Energy_1_AESTHEMOS")

DataSet <- DataSet %>%
  rename("GamesAsArt?Y/N"=`Task. Did_you_ever_ex.._`) %>%
  rename("DescriptionOfExperience"=`Description. Please_bring_to.._`) %>%
  rename("GameTitle"=`Game. What_is_the_tit.._`) %>%
  rename("WhyIsThisExperienceArt?"=`Whyart. In_your_opinion.._`)

names(DataSet)[32:52] <- AESTHEMOS1
names(DataSet)[53:73] <- AESTHEMOS2
  
```


#__Removing Participants__#
```{r}

DataSet_RM <- DataSet %>%
  #Removing all Test Data (Any "participant" coming from the Lime Survey Admin Page)#
  filter(str_detect(`refurl. Referrer_URL`, "admin", negate = TRUE)) %>%
  #Removing all people who didn't finish (I.e., ended before the check for bonus questions (page 10))
  filter(`lastpage. Last_page`>=10) %>%
  #Removing anybody who did not give consent
  filter(`InformedConsent[IC1]. Informed_Consen..__[I_have_read_and.._]` =="Yes" & 
           `InformedConsent[IC2]. Informed_Consen..__[I_agree_to_part.._]`=="Yes" & 
           `InformedConsent[IC3]. Informed_Consen..__[I_understand_th.._]`=="Yes" & 
           `InformedConsent[IC4]. Informed_Consen..__[I_understand_th.._]`=="Yes" & 
           `InformedConsent[IC5]. Informed_Consen..__[I_understand_an.._]`=="Yes" & 
           `InformedConsent[IC6]. Informed_Consen..__[I_am_at_least_1.._]`=="Yes") %>%
  #Removing anybody younger than 18
  filter(!`Age. How_old_are_you?`<18) %>%
  #Removing anyone with an English level <3
  filter(`EnglishLevel. On_a_scale_from.._`>2)

DataSet_Removed_Lastpage <- DataSet %>%
  filter(`lastpage. Last_page`<10)

DataSet_Removed_Consent <- DataSet %>%
  #Removing all Test Data (Any "participant" coming from the Lime Survey Admin Page)#
  filter(str_detect(`refurl. Referrer_URL`, "admin", negate = TRUE)) %>%
  #Removing all people who didn't finish (I.e., ended before the check for bonus questions (page 10))
  filter(`lastpage. Last_page`>=10) %>%
  #Removing anybody who did not give consent
  filter(!`InformedConsent[IC1]. Informed_Consen..__[I_have_read_and.._]` =="Yes" | 
           !`InformedConsent[IC2]. Informed_Consen..__[I_agree_to_part.._]`=="Yes" | 
           !`InformedConsent[IC3]. Informed_Consen..__[I_understand_th.._]`=="Yes" | 
           !`InformedConsent[IC4]. Informed_Consen..__[I_understand_th.._]`=="Yes" | 
           !`InformedConsent[IC5]. Informed_Consen..__[I_understand_an.._]`=="Yes")

DataSet_Removed_Age <- DataSet %>%
  #Removing all Test Data (Any "participant" coming from the Lime Survey Admin Page)#
  filter(str_detect(`refurl. Referrer_URL`, "admin", negate = TRUE)) %>%
  #Removing all people who didn't finish (I.e., ended before the check for bonus questions (page 10))
  filter(`lastpage. Last_page`>=10) %>%
  #Removing anybody who did not give consent
  filter(`InformedConsent[IC1]. Informed_Consen..__[I_have_read_and.._]` =="Yes" & 
           `InformedConsent[IC2]. Informed_Consen..__[I_agree_to_part.._]`=="Yes" & 
           `InformedConsent[IC3]. Informed_Consen..__[I_understand_th.._]`=="Yes" & 
           `InformedConsent[IC4]. Informed_Consen..__[I_understand_th.._]`=="Yes" & 
           `InformedConsent[IC5]. Informed_Consen..__[I_understand_an.._]`=="Yes") %>%
  filter(`Age. How_old_are_you?` < 18 | 
           !`InformedConsent[IC6]. Informed_Consen..__[I_am_at_least_1.._]`=="Yes")
  
```

#__Removing Junk Columns__#
```{r}
DataSet_Cleaned <- DataSet_RM %>%
  select(!`submitdate. Date_submitted`:`InformedConsent[IC6]. Informed_Consen..__[I_am_at_least_1.._]`) %>%
  select(!`Task2. Please_bring_to.._`) %>%
  select(!`NoIC. Thank_you_for_y.._`) %>%
  select(!`Success. Thank_you_very_.._`)
```

#__Fixing <2 months ago was saved as N/A by LimeSurvey__#
```{r}
#As this question was mandatory, each participant who has seen this question, must have chosen an answer. If they had not answered this question, the other questions on this page have to be NA to. As these were deemed incomplete, they were not exported into the raw data file. Therefore we can be sure, that if participants indicated they experienced games as art (`GamesAsArt?Y/N` == "Yes") and LongAgo is Na(is.na(DataSet_Cleaned$`LongAgo. How_long_ago_di.._`)) the particpants chose "<2 months ago"!
DataSet_Cleaned$`LongAgo. How_long_ago_di.._`[DataSet_Cleaned$`GamesAsArt?Y/N` == "Yes" & is.na(DataSet_Cleaned$`LongAgo. How_long_ago_di.._`)] <- "<2 months ago"
```



##__Creating Latent Class Analysis DataSet__##
```{r}
##Extract all the relevant Columns for the network analysis
DataSet_NetworkAnalysis <- DataSet_Cleaned %>%
  select(`id. Response_ID`, +
  #AesthemosData
    ends_with("_AESTHEMOS"), +
  #DemographicData
    2:5, +
  #Expertise
    63:88
    )


##Save DataSet as CSV in folder MainAnalyses/NetworkAnalysis
write.csv(DataSet_NetworkAnalysis, file = "../MainAnalyses/LatentClassAnalysis/NetworkAnalysis_DataFile.csv")
```

##_Creating Qualitative Data Analysis DataSet__#
```{r}
##Extract all the relevant columns for the qualitative Data Analysis
DataSet_Qualitative <- DataSet_Cleaned %>%
  arrange(`GamesAsArt?Y/N`) %>%
  select(`id. Response_ID`, +
  #Qualitative Data
  6:13,  +
  #Bonus Questions  
  90:98, +
  #No Art Experience  
  14:19, +
  #Favourite Games  
  82:86  
  )  
    
##Save DataSet as CSV in Folder
write.csv(DataSet_Qualitative, file = "../MainAnalyses/QualitativeAnalysis/QualitativeAnalysis_DataFile.csv")
```

##_Save a clean DataSet for Descriptive Analyses__#
```{r}
DataSet_Descriptive <- DataSet_Cleaned;

##Save DataSet as CSV in Folder
write.csv(DataSet_Descriptive, file = "../MainAnalyses/DescriptiveHollisticAnalysis/DescriptiveAnalysis_DataFile.csv")
```