---
title: "Analysis: Themes and Expertise"
author: "Anonymous"
date: "13 8 2020"
output: 
  html_document:
    theme: sandstone
editor_options: 
  chunk_output_type: console
---



```{r setup, include=TRUE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```



This doc gives some exploratory insight into the Themes and Expertise


```{r  include=FALSE}

# Setup: Always Run!
# This gets all packages and the file.

if(!require(tidyverse)){install.packages('tidyverse')}
if(!require(readxl)){install.packages('readxl')}
if(!require(summarytools)){install.packages('summarytools')}
if(!require(patchwork)){install.packages('patchwork')}
if(!require(ggsignif)){install.packages('ggsignif')}
if(!require(reshape2)){install.packages('reshape2')}
if(!require(viridis)){install.packages("viridis")}
if(!require(LaplacesDemon)){install.packages("LaplacesDemon")}
library(tidyverse, summarytools)
library(readxl)
library(patchwork)
library(ggsignif)
library(reshape2)
library(viridis)
library(LaplacesDemon)
##Set Working DIR so Input&Output is correct
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))


CIFunction <- function(value, n, CritNumber) {
  CritNumber*sd(value, na.rm=TRUE)*(sqrt((n-1)/n)) / sqrt(n)
}

```



```{r}
#Import Data Sets
##Note: This requires the complete Analysis Folder

#Get Thmese
Themes_DF <- read_xlsx("Themes-Expertise.xlsx")

#Get Expertise Measures
DataSet <- read.csv("../../../DescriptiveHollisticAnalysis/DescriptiveAnalysis_DataFile.csv")
Expertise_DF <- DataSet %>%
  select(`id..Response_ID`,
         `Years..For_how_many_ye.._`, `HoursPerWeek..How_many_hours_.._`,
           `ExperienceGeneral.SQ001...Please_rate_the..__.I_am_experience.._.`, `ExperienceGeneral.SQ003...Please_rate_the..__.As_how_broad_wo.._.`, 
         `OccupationVG..Do_you_currentl.._`, `OccupationArt..Do_you_currentl.._`) %>%
  rename(OccupationVG = `OccupationVG..Do_you_currentl.._`) %>%
  rename(OccupationArt = `OccupationArt..Do_you_currentl.._`)

ThemesExpertise_DF <- full_join(Themes_DF, Expertise_DF, by ="id..Response_ID")
```


## Did Professionals name more topics:

First, we separated experts(`r nrow(ThemesExpertise_DF %>% filter(OccupationVG == "Yes"))`) and non-experts(`r nrow(ThemesExpertise_DF %>% filter(OccupationVG == "No"))`) by their occupational status


```{r}
#Create Count:
ThemesExpertise_DF <- ThemesExpertise_DF %>%
  mutate(Count_Themes = `The Feels`+`Expressive potential of games`+craft+`exploration of interpretation`+`the thinks`+`visual beauty`+`all games art`)

ggplot(ThemesExpertise_DF, aes(ThemesExpertise_DF$OccupationVG, ThemesExpertise_DF$Count_Themes)) +
  geom_violin() +
  geom_boxplot(width=0.1) +
  xlab("Expert") + 
  ylab("Themes Mentioned")

CountOfThemesMentioned <- data.frame(table(ThemesExpertise_DF$Count_Themes))

```
Of our 174 participants, `r CountOfThemesMentioned[1,2]` mentioned `r CountOfThemesMentioned[1,1]`, `r CountOfThemesMentioned[2,2]` mentioned `r CountOfThemesMentioned[2,1]`, `r CountOfThemesMentioned[3,2]` mentioned `r CountOfThemesMentioned[3,1]`, and `r CountOfThemesMentioned[4,2]` mentioned `r CountOfThemesMentioned[4,1]` themes.


## Which Themes were mentioned how often by which group?


```{r}

nThemes <- data.frame(nAllGamesArt = sum(Themes_DF$`all games art`),
                      nCraft = sum(Themes_DF$craft),
                      nExploration = sum(Themes_DF$`exploration of interpretation`),
                      nExpressive = sum(Themes_DF$`Expressive potential of games`),
                      nFeels = sum(Themes_DF$`The Feels`),
                      nThinks = sum(Themes_DF$`the thinks`),
                      nBeauty = sum(Themes_DF$`visual beauty`))

JobExpert_DF <- ThemesExpertise_DF %>%
  select(14, 3:9) %>%
  pivot_longer(2:8, names_to="Theme", values_to = "Sum") %>%
  #Renaming is done per hand from nThemes as fct_recode doesn't play well with Parse
    mutate(`Theme` = fct_recode(`Theme`, "All Games Are Art (yes = 9)" = "all games art",
                                 "Craft (yes = 66)" = "craft",
                                 "Exploration Of Interpretation (yes = 10)" = "exploration of interpretation",
                                 "Expressive Potential of Games (yes = 51)" = "Expressive potential of games",
                                 "The Feels (yes = 59)" = "The Feels",
                                 "The Thinks (yes = 19)" = "the thinks",
                                 "Visual Beauty (yes = 37)" = "visual beauty")) %>%
  group_by(OccupationVG, `Theme`) %>%
  summarize(total = sum(`Sum`))

JobExpert_DF_Pivot <- JobExpert_DF %>%
  mutate(percent = ifelse(OccupationVG == "Yes", 
                   `total`*100/nrow(ThemesExpertise_DF %>% filter(OccupationVG == "Yes")), 
                   `total`*100/nrow(ThemesExpertise_DF %>% filter(OccupationVG == "No"))))

#Annotations for differences and Y positions

annotationsJobExpert <- as.numeric(
  c(JobExpert_DF_Pivot[8,4]-JobExpert_DF_Pivot[1,4],JobExpert_DF_Pivot[9,4]-JobExpert_DF_Pivot[2,4],JobExpert_DF_Pivot[10,4]-JobExpert_DF_Pivot[3,4],
                 JobExpert_DF_Pivot[11,4]-JobExpert_DF_Pivot[4,4],JobExpert_DF_Pivot[12,4]-JobExpert_DF_Pivot[5,4],JobExpert_DF_Pivot[13,4]-JobExpert_DF_Pivot[6,4],
                 JobExpert_DF_Pivot[14,4]-JobExpert_DF_Pivot[7,4]))

yPositionsJobExpert <- c(as.numeric(JobExpert_DF_Pivot[8,4])+15, as.numeric(JobExpert_DF_Pivot[9,4])+15, as.numeric(JobExpert_DF_Pivot[10,4])+15,
                             as.numeric(JobExpert_DF_Pivot[11,4])+15, as.numeric(JobExpert_DF_Pivot[12,4])+15,
                             as.numeric(JobExpert_DF_Pivot[13,4])+15, as.numeric(JobExpert_DF_Pivot[7,4])+15)


#ggplot(JobExpert_DF_Pivot, aes(`Theme`, percent, fill = OccupationVG)) +
#  geom_bar(stat = "identity", position = "dodge") +
#  ggtitle("Professional Split") +
#  scale_fill_manual(name="Expert", values=c("#dd4613","#A71C49")) +  
#  geom_signif(xmin=c(0.8, 1.8, 2.8, 3.8, 4.8, 5.8, 6.8), xmax=c(1.2,2.2,3.2,4.2,5.2,6.2,7.2),
#              y_position = yPositionsJobExpert,
#              annotation = round(annotationsJobExpert,2)) +
#  ylim(0, 100) +
#  coord_flip()
  

##Professional Expertise
Professionals_DF <- ThemesExpertise_DF %>%
  select(14,15,3:9) %>%
  mutate(expert = ifelse(OccupationVG == "Yes" & OccupationArt == "Yes", "Both",
                         ifelse(OccupationVG == "Yes" & OccupationArt == "No", "VG Professional",
                                ifelse(OccupationVG == "No" & OccupationArt == "Yes", "Art Professional",
                                       ifelse(OccupationVG == "No" & OccupationArt == "No","Layperson",NA))))) %>%
  select(!1:2) %>%
  group_by(expert)
Professionals_DF_melted <- melt(Professionals_DF, measure.vars = c(1:7))


Professionals_DF_summarized <- Professionals_DF_melted %>%
  group_by(expert, variable) %>%
  summarize(Sum = sum(value)) %>%
  mutate(percent =
           ifelse(expert=="Both", Sum*100/nrow(ThemesExpertise_DF %>% filter(OccupationVG == "Yes" & OccupationArt == "Yes")),
            ifelse(expert=="Art Professional", Sum*100/nrow(ThemesExpertise_DF %>% filter(OccupationVG == "No" & OccupationArt == "Yes")),
             ifelse(expert=="VG Professional", Sum*100/nrow(ThemesExpertise_DF %>% filter(OccupationVG == "Yes" & OccupationArt == "No")),
              ifelse(expert=="Layperson", Sum*100/nrow(ThemesExpertise_DF %>% filter(OccupationVG == "No" & OccupationArt == "No")),
                     NA))))
         )


Professionals_DF_summarized$expert <- fct_relevel(Professionals_DF_summarized$expert, "Both", "VG Professional", "Art Professional", "Layperson")
Professionals_DF_summarized$expert <- fct_recode(Professionals_DF_summarized$expert, "Both (16)" = "Both",
                                                 "VG Professional (9)" = "VG Professional",
                                                 "Art Professional (33)" = "Art Professional",
                                                 "Layperson (116)" = "Layperson")


ggplot(Professionals_DF_summarized, aes(variable, percent, fill = expert)) +
  geom_bar(stat = "identity", position = "dodge") +
  ggtitle("Professional Split") +
  scale_fill_viridis(discrete=TRUE, name="Profession") +
  ylim(0, 100) +
  theme(legend.position = c(.8,0.8)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))

```


Split by person identifying as a professional member of the games industry or the art industry and by people who identify as neither:

```{r}

##All Professionals
Professionals_DF <- ThemesExpertise_DF %>%
  select(14,15,3:9) %>%
  mutate(expert = ifelse(OccupationVG == "Yes" & OccupationArt == "Yes", "Professional",
                         ifelse(OccupationVG == "Yes" & OccupationArt == "No", "Professional",
                                ifelse(OccupationVG == "No" & OccupationArt == "Yes", "Professional",
                                       ifelse(OccupationVG == "No" & OccupationArt == "No","Layperson",NA))))) %>%
  select(!1:2) %>%
  group_by(expert)

Professionals_DF_melted <- melt(Professionals_DF, measure.vars = c(1:7))

Professionals_DF_summarized <- Professionals_DF_melted %>%
  group_by(expert, variable) %>%
  summarize(Sum = sum(value)) %>%
  mutate(percent =
           ifelse(expert=="Professional", Sum*100/nrow(ThemesExpertise_DF %>% filter(OccupationVG != "No" | OccupationArt != "No")),
              ifelse(expert=="Layperson", Sum*100/nrow(ThemesExpertise_DF %>% filter(OccupationVG == "No" & OccupationArt == "No")),
                     NA))
         )


#Annotations for differences and Y positions
annotationsProfessionals <- as.numeric(
  c(Professionals_DF_summarized[8,4]-Professionals_DF_summarized[1,4],Professionals_DF_summarized[9,4]-Professionals_DF_summarized[2,4],Professionals_DF_summarized[10,4]-Professionals_DF_summarized[3,4],
                 Professionals_DF_summarized[11,4]-Professionals_DF_summarized[4,4],Professionals_DF_summarized[12,4]-Professionals_DF_summarized[5,4],Professionals_DF_summarized[13,4]-Professionals_DF_summarized[6,4],
                 Professionals_DF_summarized[14,4]-Professionals_DF_summarized[7,4]))

yProfessionals <- c(as.numeric(Professionals_DF_summarized[1,4])+5, as.numeric(Professionals_DF_summarized[9,4])+5, as.numeric(Professionals_DF_summarized[3,4])+5,
                             as.numeric(Professionals_DF_summarized[11,4])+5, as.numeric(Professionals_DF_summarized[12,4])+5,
                             as.numeric(Professionals_DF_summarized[6,4])+5, as.numeric(Professionals_DF_summarized[7,4])+5)




ggplot(Professionals_DF_summarized, aes(variable, percent, fill = expert)) +
  geom_bar(stat = "identity", position = "dodge") +
  ggtitle("Professional Split") +
  geom_signif(xmin=c(0.8, 1.8, 2.8, 3.8, 4.8, 5.8, 6.8), xmax=c(1.2,2.2,3.2,4.2,5.2,6.2,7.2),
              y_position = yProfessionals,
              annotation = round(annotationsProfessionals,2))+
  scale_fill_viridis( discrete = TRUE, option = "D",
    labels=c(paste("Layperson (", nrow(Professionals_DF %>% filter(expert=="Layperson")), ")", sep=""), 
             paste("Expert (", nrow(Professionals_DF %>% filter(expert=="Professional")), ")", sep="")),
    name="Profession") +
  ylim(0, 100) +
  theme(legend.position = c(0.3,0.8)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1))
  



```

## Self Reported Expertise

As professionalism does not have an exclusivity to expertise, we further looked at the self reported expertise:


```{r}
#View Self Reported Expertise:
ggplot(ThemesExpertise_DF %>% filter(!is.na(ExperienceGeneral.SQ001...Please_rate_the..__.I_am_experience.._.)), 
        aes(`ExperienceGeneral.SQ001...Please_rate_the..__.I_am_experience.._.`)) + 
        geom_histogram(binwidth = 5, fill="#A71C49") +
        xlab("Self Reported Experience")
```


The distribution of self reported expertise is rather skewed to the right, with many participants rating themselves at the top end of the scale. Therefore a median and mean split result in a rather high cut-off point.


```{r}
#Performing a median split to determine Expertise and selecting relevant Columns
Median_DF <- ThemesExpertise_DF %>%
  mutate(SelfReportExpert = ifelse(
    `ExperienceGeneral.SQ001...Please_rate_the..__.I_am_experience.._.`<=median(`ExperienceGeneral.SQ001...Please_rate_the..__.I_am_experience.._.`, na.rm=TRUE),
    "No", "Yes")) %>%
  select(SelfReportExpert, 3:9) %>%
  filter(!is.na(SelfReportExpert))

#Pivoting
Median_DF_Pivot <- Median_DF %>%
  pivot_longer(2:8, names_to="Theme", values_to = "Sum") %>%
  #Renaming is done per hand from nThemes as fct_recode doesn't play well with Parse
  mutate(`Theme` = fct_recode(`Theme`, "All Games Are Art (yes = 9)" = "all games art",
                               "Craft (yes = 66)" = "craft",
                               "Exploration Of Interpretation (yes = 10)" = "exploration of interpretation",
                               "Expressive Potential of Games (yes = 51)" = "Expressive potential of games",
                               "The Feels (yes = 59)" = "The Feels",
                               "The Thinks (yes = 19)" = "the thinks",
                               "Visual Beauty (yes = 37)" = "visual beauty")) %>%
  group_by(SelfReportExpert, `Theme`) %>%
  summarize(total = sum(`Sum`))

#Compute percent to deal with differences in N
Median_DF_Pivot <- Median_DF_Pivot %>%
  mutate(percent = ifelse(SelfReportExpert == "Yes", 
                   `total`*100/nrow(Median_DF %>% filter(Median_DF$SelfReportExpert == "Yes")), 
                   `total`*100/nrow(Median_DF %>% filter(Median_DF$SelfReportExpert == "No"))))

#Annotations for differences and Y positions

annotationsMedian <- as.numeric(
  c(Median_DF_Pivot[8,4]-Median_DF_Pivot[1,4],Median_DF_Pivot[9,4]-Median_DF_Pivot[2,4],Median_DF_Pivot[10,4]-Median_DF_Pivot[3,4],
                 Median_DF_Pivot[11,4]-Median_DF_Pivot[4,4],Median_DF_Pivot[12,4]-Median_DF_Pivot[5,4],Median_DF_Pivot[13,4]-Median_DF_Pivot[6,4],
                 Median_DF_Pivot[14,4]-Median_DF_Pivot[7,4]))

yPositionsMedian <- c(as.numeric(Median_DF_Pivot[8,4])+15, as.numeric(Median_DF_Pivot[9,4])+15, as.numeric(Median_DF_Pivot[10,4])+15,
                             as.numeric(Median_DF_Pivot[11,4])+15, as.numeric(Median_DF_Pivot[12,4])+15,
                             as.numeric(Median_DF_Pivot[13,4])+15, as.numeric(Median_DF_Pivot[14,4])+15)


MedianSplitPlot <- ggplot(Median_DF_Pivot, aes(`Theme`, percent, fill = SelfReportExpert)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_viridis(name="Expert", discrete=TRUE) +
  ggtitle("Median Split") +
  ylim(0, 100) +
  geom_signif(xmin=c(0.8, 1.8, 2.8, 3.8, 4.8, 5.8, 6.8), xmax=c(1.2,2.2,3.2,4.2,5.2,6.2,7.2),
              y_position = yPositionsMedian,
              annotation = round(annotationsMedian,2)) +
  coord_flip()

median_SelfReportExpert <- median(ThemesExpertise_DF$ExperienceGeneral.SQ001...Please_rate_the..__.I_am_experience.._., na.rm=TRUE)
mean_SelfReportExpert <- mean(ThemesExpertise_DF$ExperienceGeneral.SQ001...Please_rate_the..__.I_am_experience.._., na.rm=TRUE)
```


We perform a median (`r median_SelfReportExpert`) split to differentiate between self reported experts (`r nrow(Median_DF %>% filter(SelfReportExpert == "Yes"))`) and non-experts(`r nrow(Median_DF %>% filter(SelfReportExpert == "No"))`):


```{r}
print(MedianSplitPlot)
```




```{r}
#Performing a mean split to determine Expertise and selecting relevant Columns
Mean_DF <- ThemesExpertise_DF %>%
  mutate(SelfReportExpert = ifelse(
    `ExperienceGeneral.SQ001...Please_rate_the..__.I_am_experience.._.`<=mean(`ExperienceGeneral.SQ001...Please_rate_the..__.I_am_experience.._.`, na.rm=TRUE),
    "No", "Yes")) %>%
  select(SelfReportExpert, 3:9) %>%
  filter(!is.na(SelfReportExpert))

#Pivoting
Mean_DF_Pivot <- Mean_DF %>%
  pivot_longer(2:8, names_to="Theme", values_to = "Sum") %>%
  #Renaming is done per hand from nThemes as fct_recode doesn't play well with Parse
  mutate(`Theme` = fct_recode(`Theme`, "All Games Are Art (yes = 9)" = "all games art",
                               "Craft (yes = 66)" = "craft",
                               "Exploration Of Interpretation (yes = 10)" = "exploration of interpretation",
                               "Expressive Potential of Games (yes = 51)" = "Expressive potential of games",
                               "The Feels (yes = 59)" = "The Feels",
                               "The Thinks (yes = 19)" = "the thinks",
                               "Visual Beauty (yes = 37)" = "visual beauty")) %>%
  group_by(SelfReportExpert, `Theme`) %>%
  summarize(total = sum(`Sum`))

#Compute percent to deal with differences in N
Mean_DF_Pivot <- Mean_DF_Pivot %>%
  mutate(percent = ifelse(SelfReportExpert == "Yes", 
                   `total`*100/nrow(Median_DF %>% filter(Mean_DF$SelfReportExpert == "Yes")), 
                   `total`*100/nrow(Median_DF %>% filter(Mean_DF$SelfReportExpert == "No"))))

#Annotations an Y Positions
annotationsMean <- as.numeric(
  c(Mean_DF_Pivot[8,4]-Mean_DF_Pivot[1,4],Mean_DF_Pivot[9,4]-Mean_DF_Pivot[2,4],Mean_DF_Pivot[10,4]-Mean_DF_Pivot[3,4],
                 Mean_DF_Pivot[11,4]-Mean_DF_Pivot[4,4],Mean_DF_Pivot[12,4]-Mean_DF_Pivot[5,4],Mean_DF_Pivot[13,4]-Mean_DF_Pivot[6,4],
                 Mean_DF_Pivot[14,4]-Mean_DF_Pivot[7,4]))

yPositionsMean <- c(as.numeric(Mean_DF_Pivot[8,4])+15, as.numeric(Mean_DF_Pivot[9,4])+15, as.numeric(Mean_DF_Pivot[10,4])+15,
                             as.numeric(Mean_DF_Pivot[11,4])+15, as.numeric(Mean_DF_Pivot[12,4])+15,
                             as.numeric(Mean_DF_Pivot[13,4])+15, as.numeric(Mean_DF_Pivot[14,4])+15)


MeanSplitPlot <- ggplot(Mean_DF_Pivot, aes(`Theme`, percent, fill = SelfReportExpert)) +
  geom_bar(stat = "identity", position = "dodge") +
  ggtitle("Mean Split") +
  scale_fill_viridis(name="Expert", discrete=TRUE) +
  ylim(0, 100) +
  geom_signif(xmin=c(0.8, 1.8, 2.8, 3.8, 4.8, 5.8, 6.8), xmax=c(1.2,2.2,3.2,4.2,5.2,6.2,7.2),
              y_position = yPositionsMean,
              annotation = round(annotationsMean,2)) +
  coord_flip()
```


Therefore we further performed a split around the mean (`r round(mean_SelfReportExpert, 2)`) resulting in `r nrow(Mean_DF %>% filter(SelfReportExpert == "Yes"))` experts and `r nrow(Mean_DF %>% filter(SelfReportExpert == "No"))` non-experts:


```{r}
print(MeanSplitPlot)
```



```{r}
#Performing a middle split to determine Expertise and selecting relevant Columns
Middle_DF <- ThemesExpertise_DF %>%
  mutate(SelfReportExpert = ifelse(
    `ExperienceGeneral.SQ001...Please_rate_the..__.I_am_experience.._.`<= 50,
    "No", "Yes")) %>%
  select(SelfReportExpert, 3:9) %>%
  filter(!is.na(SelfReportExpert))

#Pivoting
Middle_DF_Pivot <- Middle_DF %>%
  pivot_longer(2:8, names_to="Theme", values_to = "Sum") %>%
  #Renaming is done per hand from nThemes as fct_recode doesn't play well with Parse
  mutate(`Theme` = fct_recode(`Theme`, "All Games Are Art (yes = 9)" = "all games art",
                               "Craft (yes = 66)" = "craft",
                               "Exploration Of Interpretation (yes = 10)" = "exploration of interpretation",
                               "Expressive Potential of Games (yes = 51)" = "Expressive potential of games",
                               "The Feels (yes = 59)" = "The Feels",
                               "The Thinks (yes = 19)" = "the thinks",
                               "Visual Beauty (yes = 37)" = "visual beauty")) %>%
  group_by(SelfReportExpert, `Theme`) %>%
  summarize(total = sum(`Sum`))

#Compute percent to deal with differences in N
Middle_DF_Pivot <- Middle_DF_Pivot %>%
  mutate(percent = ifelse(SelfReportExpert == "Yes", 
                   `total`*100/nrow(Median_DF %>% filter(Middle_DF$SelfReportExpert == "Yes")), 
                   `total`*100/nrow(Median_DF %>% filter(Middle_DF$SelfReportExpert == "No"))))


#Annotations for differences and yPositions
annotationsMiddle <- as.numeric(
  c(Middle_DF_Pivot[8,4]-Middle_DF_Pivot[1,4],Middle_DF_Pivot[9,4]-Middle_DF_Pivot[2,4],Middle_DF_Pivot[10,4]-Middle_DF_Pivot[3,4],
                 Middle_DF_Pivot[11,4]-Middle_DF_Pivot[4,4],Middle_DF_Pivot[12,4]-Middle_DF_Pivot[5,4],Middle_DF_Pivot[13,4]-Middle_DF_Pivot[6,4],
                 Middle_DF_Pivot[14,4]-Middle_DF_Pivot[7,4]))

yPositionsMiddle <- c(as.numeric(Middle_DF_Pivot[8,4])+15, as.numeric(Middle_DF_Pivot[2,4])+15, as.numeric(Middle_DF_Pivot[10,4])+15,
                             as.numeric(Middle_DF_Pivot[11,4])+15, as.numeric(Middle_DF_Pivot[12,4])+15,
                             as.numeric(Middle_DF_Pivot[13,4])+15, as.numeric(Middle_DF_Pivot[14,4])+15)


MiddleSplitPlot <- ggplot(Middle_DF_Pivot, aes(`Theme`, percent, fill = SelfReportExpert)) +
  geom_bar(stat = "identity", position = "dodge") +
  ggtitle("Middle Split") +
  scale_fill_viridis(name="Expert", discrete=TRUE) +
  ylim(0, 100) +
  geom_signif(xmin=c(0.8, 1.8, 2.8, 3.8, 4.8, 5.8, 6.8), xmax=c(1.2,2.2,3.2,4.2,5.2,6.2,7.2),
              y_position = yPositionsMiddle,
              annotation = round(annotationsMiddle,2)) +
  coord_flip()
```


And the middle of the scale (50) resulting in `r nrow(Middle_DF %>% filter(SelfReportExpert == "Yes"))` experts and `r nrow(Middle_DF %>% filter(SelfReportExpert == "No"))` non-experts:


```{r}
print(MiddleSplitPlot)
```


## Relationship between the Themes


```{r fig.height=8, fig.width=8}
#Only Take the Themes
cor_DF <- ThemesExpertise_DF %>%
  select(3:9)

corMat <- round(cor(cor_DF, method = "pearson"), 2)
corMat[upper.tri(corMat)] <- NA
meltedCorMat <- melt(corMat, na.rm = TRUE)


ggplot(data = meltedCorMat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(color="white") +
  theme(panel.background = element_blank()) +
  ggtitle("Themes Correlations") +
  xlab("") +
  ylab("") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 12, hjust = 1)) +
  scale_fill_viridis(limit = c(-1,1),
                       name= expression(paste("Pearson ", phi))) +
  geom_text(aes(Var1, Var2, label = value), color = "black", size = 4) +
  theme(legend.direction = "horizontal", legend.position = c(0.3,0.82)) +
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5)) +
  coord_fixed()


#Additional Scatter PLots
ggpairs(cor_DF, 
        upper= list(discrete="ratio"), 
        lower= list(continuous=wrap("points", position=position_jitter(height=.3, width=.3))),
        diag=list(discrete="blankDiag")
        )
```


## Themes and AESTHEMOS 
```{r}

#Get The AESTHEMOS Items from the NetworkDataSet
AESTHEMOS_DF <- read.csv("../../../LatentClassAnalysis/NetworkAnalysis_DataFile.csv")

AESTHEMOS_DF <- AESTHEMOS_DF %>%
  select(2, ends_with("_AESTHEMOS"))

#Combine with themes
ThemesAESTHEMOS_DF <- full_join(Themes_DF,AESTHEMOS_DF, by="id..Response_ID")
```



```{r}
ThemesAESTHEMOS_DF_Pivot_Help <- ThemesAESTHEMOS_DF %>%
  select(!1:2)

ThemesAESTHEMOS_DF_Pivot <- ThemesAESTHEMOS_DF_Pivot_Help %>%
  pivot_longer(1:7, names_to = "Thematic", values_to = "Yes/No") %>%
  mutate(`Yes/No`=as.factor(`Yes/No`)) %>%
  mutate(`Thematic`=as.factor(`Thematic`)) %>%
  #This is done manually from the nThemes data frame as fct_recode doesn't work with parse
  mutate(`Thematic` = fct_recode(`Thematic`, "All Games Are Art (9)" = "all games art",
                                 "Craft (66)" = "craft",
                                 "Exploration Of Interpretation (10)" = "exploration of interpretation",
                                 "Expressive Potential of Games (51)" = "Expressive potential of games",
                                 "The Feels (59)" = "The Feels",
                                 "The Thinks (19)" = "the thinks",
                                 "Visual Beauty (37)" = "visual beauty")) %>%
  group_by(`Thematic`, `Yes/No`) %>%
  summarize_if(is.numeric, list(~mean(., na.rm=TRUE), ~sd(., na.rm=TRUE)), na.rm=TRUE)


##Create Tables for each AESTHEMOS Factor:
FeelingOfBeauty <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         FeelingOfBeauty_1_AESTHEMOS_mean, FeelingOfBeauty_1_AESTHEMOS_sd,
         FeelingOfBeauty_2_AESTHEMOS_mean, FeelingOfBeauty_2_AESTHEMOS_sd) %>%
  mutate(Mean_FeelingOfBeauty = (`FeelingOfBeauty_1_AESTHEMOS_mean` + `FeelingOfBeauty_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_FeelingOfBeauty = sqrt((`FeelingOfBeauty_1_AESTHEMOS_sd`^2 + `FeelingOfBeauty_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_LikedIt" = FeelingOfBeauty_1_AESTHEMOS_mean) %>%
  rename("SD_LikedIt" = FeelingOfBeauty_1_AESTHEMOS_sd) %>%
  rename("Mean_Beautiful" = FeelingOfBeauty_2_AESTHEMOS_mean) %>%
  rename("SD_Beautiful" = FeelingOfBeauty_2_AESTHEMOS_sd)

Fascination <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Fascination_1_AESTHEMOS_mean, Fascination_1_AESTHEMOS_sd,
         Fascination_2_AESTHEMOS_mean, Fascination_2_AESTHEMOS_sd) %>%
  mutate(Mean_Fascination = (`Fascination_1_AESTHEMOS_mean` + `Fascination_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Fascination = sqrt((`Fascination_1_AESTHEMOS_sd`^2 + `Fascination_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Impressed" = Fascination_1_AESTHEMOS_mean) %>%
  rename("SD_Impressed" = Fascination_1_AESTHEMOS_sd) %>%
  rename("Mean_Fascinated" = Fascination_2_AESTHEMOS_mean) %>%
  rename("SD_Fascinated" = Fascination_2_AESTHEMOS_sd)

BeingMoved <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         BeingMoved_1_AESTHEMOS_mean, BeingMoved_1_AESTHEMOS_sd,
         BeingMoved_2_AESTHEMOS_mean, BeingMoved_2_AESTHEMOS_sd) %>%
  mutate(Mean_BeingMoved = (`BeingMoved_1_AESTHEMOS_mean` + `BeingMoved_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_BeingMoved = sqrt((`BeingMoved_1_AESTHEMOS_sd`^2 + `BeingMoved_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_DeeplyMoved" = BeingMoved_1_AESTHEMOS_mean) %>%
  rename("SD_DeeplyMoved" = BeingMoved_1_AESTHEMOS_sd) %>%
  rename("Mean_Touched" = BeingMoved_2_AESTHEMOS_mean) %>%
  rename("SD_Touched" = BeingMoved_2_AESTHEMOS_sd)

Awe <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Awe_1_AESTHEMOS_mean, Awe_1_AESTHEMOS_sd,
         Awe_2_AESTHEMOS_mean, Awe_2_AESTHEMOS_sd) %>%
  mutate(Mean_Awe = (`Awe_1_AESTHEMOS_mean` + `Awe_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Awe = sqrt((`Awe_1_AESTHEMOS_sd`^2 + `Awe_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Sublime" = Awe_1_AESTHEMOS_mean) %>%
  rename("SD_Sublime" = Awe_1_AESTHEMOS_sd) %>%
  rename("Mean_FeltAwe" = Awe_2_AESTHEMOS_mean) %>%
  rename("SD_FeltAwe" = Awe_2_AESTHEMOS_sd)

Enchantment <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Enchantment_1_AESTHEMOS_mean, Enchantment_1_AESTHEMOS_sd,
         Enchantment_2_AESTHEMOS_mean, Enchantment_2_AESTHEMOS_sd) %>%
  mutate(Mean_Enchantment = (`Enchantment_1_AESTHEMOS_mean` + `Enchantment_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Enchantment = sqrt((`Enchantment_1_AESTHEMOS_sd`^2 + `Enchantment_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_SomethingWonderful" = Enchantment_1_AESTHEMOS_mean) %>%
  rename("SD_SomethingWonderful" = Enchantment_1_AESTHEMOS_sd) %>%
  rename("Mean_Enchanted" = Enchantment_2_AESTHEMOS_mean) %>%
  rename("SD_Enchanted" = Enchantment_2_AESTHEMOS_sd)

Nostalgia <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Nostalgia_1_AESTHEMOS_mean, Nostalgia_1_AESTHEMOS_sd,
         Nostalgia_2_AESTHEMOS_mean, Nostalgia_2_AESTHEMOS_sd) %>%
  mutate(Mean_Nostalgia = (`Nostalgia_1_AESTHEMOS_mean` + `Nostalgia_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Nostalgia = sqrt((`Nostalgia_1_AESTHEMOS_sd`^2 + `Nostalgia_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Nostalgic" = Nostalgia_1_AESTHEMOS_mean) %>%
  rename("SD_Nostalgic" = Nostalgia_1_AESTHEMOS_sd) %>%
  rename("Mean_Sentimental" = Nostalgia_2_AESTHEMOS_mean) %>%
  rename("SD_Sentimental" = Nostalgia_2_AESTHEMOS_sd)

Joy <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Joy_1_AESTHEMOS_mean, Joy_1_AESTHEMOS_sd,
         Joy_2_AESTHEMOS_mean, Joy_2_AESTHEMOS_sd) %>%
  mutate(Mean_Joy = (`Joy_1_AESTHEMOS_mean` + `Joy_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Joy = sqrt((`Joy_1_AESTHEMOS_sd`^2 + `Joy_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Delight" = Joy_1_AESTHEMOS_mean) %>%
  rename("SD_Delight" = Joy_1_AESTHEMOS_sd) %>%
  rename("Mean_Happy" = Joy_2_AESTHEMOS_mean) %>%
  rename("SD_Happy" = Joy_2_AESTHEMOS_sd)

Humor <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Humor_1_AESTHEMOS_mean, Humor_1_AESTHEMOS_sd,
         Humor_2_AESTHEMOS_mean, Humor_2_AESTHEMOS_sd) %>%
  mutate(Mean_Humor = (`Humor_1_AESTHEMOS_mean` + `Humor_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Humor = sqrt((`Humor_1_AESTHEMOS_sd`^2 + `Humor_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Amused" = Humor_1_AESTHEMOS_mean) %>%
  rename("SD_Amused" = Humor_1_AESTHEMOS_sd) %>%
  rename("Mean_Funny" = Humor_2_AESTHEMOS_mean) %>%
  rename("SD_Funny" = Humor_2_AESTHEMOS_sd)

Vitality <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Vitality_1_AESTHEMOS_mean, Vitality_1_AESTHEMOS_sd,
         Vitality_2_AESTHEMOS_mean, Vitality_2_AESTHEMOS_sd) %>%
  mutate(Mean_Vitality = (`Vitality_1_AESTHEMOS_mean` + `Vitality_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Vitality = sqrt((`Vitality_1_AESTHEMOS_sd`^2 + `Vitality_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Spurred" = Vitality_1_AESTHEMOS_mean) %>%
  rename("SD_Spurred" = Vitality_1_AESTHEMOS_sd) %>%
  rename("Mean_Invigorated" = Vitality_2_AESTHEMOS_mean) %>%
  rename("SD_Invigorated" = Vitality_2_AESTHEMOS_sd)

Energy <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Energy_1_AESTHEMOS_mean, Energy_1_AESTHEMOS_sd,
         Energy_2_AESTHEMOS_mean, Energy_2_AESTHEMOS_sd) %>%
  mutate(Mean_Energy = (`Energy_1_AESTHEMOS_mean` + `Energy_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Energy = sqrt((`Energy_1_AESTHEMOS_sd`^2 + `Energy_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Motivated" = Energy_1_AESTHEMOS_mean) %>%
  rename("SD_Motivated" = Energy_1_AESTHEMOS_sd) %>%
  rename("Mean_Energized" = Energy_2_AESTHEMOS_mean) %>%
  rename("SD_Energized" = Energy_2_AESTHEMOS_sd)

Relaxation <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Relaxation_1_AESTHEMOS_mean, Relaxation_1_AESTHEMOS_sd,
         Relaxation_2_AESTHEMOS_mean, Relaxation_2_AESTHEMOS_sd) %>%
  mutate(Mean_Relaxation = (`Relaxation_1_AESTHEMOS_mean` + `Relaxation_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Relaxation = sqrt((`Relaxation_1_AESTHEMOS_sd`^2 + `Relaxation_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Calmed" = Relaxation_1_AESTHEMOS_mean) %>%
  rename("SD_Calmed" = Relaxation_1_AESTHEMOS_sd) %>%
  rename("Mean_Relaxed" = Relaxation_2_AESTHEMOS_mean) %>%
  rename("SD_Relaxed" = Relaxation_2_AESTHEMOS_sd)

Surprise <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Surprise_1_AESTHEMOS_mean, Surprise_1_AESTHEMOS_sd,
         Surprise_2_AESTHEMOS_mean, Surprise_2_AESTHEMOS_sd) %>%
  mutate(Mean_Surprise = (`Surprise_1_AESTHEMOS_mean` + `Surprise_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Surprise = sqrt((`Surprise_1_AESTHEMOS_sd`^2 + `Surprise_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Baffled" = Surprise_1_AESTHEMOS_mean) %>%
  rename("SD_Baffled" = Surprise_1_AESTHEMOS_sd) %>%
  rename("Mean_Surprised" = Surprise_2_AESTHEMOS_mean) %>%
  rename("SD_Surprised" = Surprise_2_AESTHEMOS_sd)

Interest <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Interest_1_AESTHEMOS_mean, Interest_1_AESTHEMOS_sd,
         Interest_2_AESTHEMOS_mean, Interest_2_AESTHEMOS_sd) %>%
  mutate(Mean_Interest = (`Interest_1_AESTHEMOS_mean` + `Interest_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Interest = sqrt((`Interest_1_AESTHEMOS_sd`^2 + `Interest_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Curious" = Interest_1_AESTHEMOS_mean) %>%
  rename("SD_Curious" = Interest_1_AESTHEMOS_sd) %>%
  rename("Mean_SparkedInterest" = Interest_2_AESTHEMOS_mean) %>%
  rename("SD_SparkedInterest" = Interest_2_AESTHEMOS_sd)

IntellectualChallenge <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         IntellectualChallenge_1_AESTHEMOS_mean, IntellectualChallenge_1_AESTHEMOS_sd,
         IntellectualChallenge_2_AESTHEMOS_mean, IntellectualChallenge_2_AESTHEMOS_sd) %>%
  mutate(Mean_IntellectualChallenge = (`IntellectualChallenge_1_AESTHEMOS_mean` + `IntellectualChallenge_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_IntellectualChallenge = sqrt((`IntellectualChallenge_1_AESTHEMOS_sd`^2 + `IntellectualChallenge_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Challenged" = IntellectualChallenge_1_AESTHEMOS_mean) %>%
  rename("SD_Challenged" = IntellectualChallenge_1_AESTHEMOS_sd) %>%
  rename("Mean_Engaged" = IntellectualChallenge_2_AESTHEMOS_mean) %>%
  rename("SD_Engaged" = IntellectualChallenge_2_AESTHEMOS_sd)

Insight <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Insight_1_AESTHEMOS_mean, Insight_1_AESTHEMOS_sd,
         Insight_2_AESTHEMOS_mean, Insight_2_AESTHEMOS_sd) %>%
  mutate(Mean_Insight = (`Insight_1_AESTHEMOS_mean` + `Insight_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Insight = sqrt((`Insight_1_AESTHEMOS_sd`^2 + `Insight_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_SuddenInsight" = Insight_1_AESTHEMOS_mean) %>%
  rename("SD_SuddenInsight" = Insight_1_AESTHEMOS_sd) %>%
  rename("Mean_DeeperMeaning" = Insight_2_AESTHEMOS_mean) %>%
  rename("SD_DeeperMeaning" = Insight_2_AESTHEMOS_sd)

FeelingOfUgliness <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         FeelingOfUgliness_1_AESTHEMOS_mean, FeelingOfUgliness_1_AESTHEMOS_sd,
         FeelingOfUgliness_2_AESTHEMOS_mean, FeelingOfUgliness_2_AESTHEMOS_sd) %>%
  mutate(Mean_FeelingOfUgliness = (`FeelingOfUgliness_1_AESTHEMOS_mean` + `FeelingOfUgliness_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_FeelingOfUgliness = sqrt((`FeelingOfUgliness_1_AESTHEMOS_sd`^2 + `FeelingOfUgliness_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Distasteful" = FeelingOfUgliness_1_AESTHEMOS_mean) %>%
  rename("SD_Distasteful" = FeelingOfUgliness_1_AESTHEMOS_sd) %>%
  rename("Mean_Ugly" = FeelingOfUgliness_2_AESTHEMOS_mean) %>%
  rename("SD_Ugly" = FeelingOfUgliness_2_AESTHEMOS_sd)

Boredom <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Boredom_1_AESTHEMOS_mean, Boredom_1_AESTHEMOS_sd,
         Boredom_2_AESTHEMOS_mean, Boredom_2_AESTHEMOS_sd) %>%
  mutate(Mean_Boredom = (`Boredom_1_AESTHEMOS_mean` + `Boredom_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Boredom = sqrt((`Boredom_1_AESTHEMOS_sd`^2 + `Boredom_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Indifferent" = Boredom_1_AESTHEMOS_mean) %>%
  rename("SD_Indifferent" = Boredom_1_AESTHEMOS_sd) %>%
  rename("Mean_Bored" = Boredom_2_AESTHEMOS_mean) %>%
  rename("SD_Bored" = Boredom_2_AESTHEMOS_sd)

Confusion <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Confusion_1_AESTHEMOS_mean, Confusion_1_AESTHEMOS_sd,
         Confusion_2_AESTHEMOS_mean, Confusion_2_AESTHEMOS_sd) %>%
  mutate(Mean_Confusion = (`Confusion_1_AESTHEMOS_mean` + `Confusion_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Confusion = sqrt((`Confusion_1_AESTHEMOS_sd`^2 + `Confusion_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Confused" = Confusion_1_AESTHEMOS_mean) %>%
  rename("SD_Confused" = Confusion_1_AESTHEMOS_sd) %>%
  rename("Mean_Unsettling" = Confusion_2_AESTHEMOS_mean) %>%
  rename("SD_Unsettling" = Confusion_2_AESTHEMOS_sd)

Anger <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Anger_1_AESTHEMOS_mean, Anger_1_AESTHEMOS_sd,
         Anger_2_AESTHEMOS_mean, Anger_2_AESTHEMOS_sd) %>%
  mutate(Mean_Anger = (`Anger_1_AESTHEMOS_mean` + `Anger_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Anger = sqrt((`Anger_1_AESTHEMOS_sd`^2 + `Anger_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Aggressive" = Anger_1_AESTHEMOS_mean) %>%
  rename("SD_Aggressive" = Anger_1_AESTHEMOS_sd) %>%
  rename("Mean_Angry" = Anger_2_AESTHEMOS_mean) %>%
  rename("SD_Angry" = Anger_2_AESTHEMOS_sd)

Uneasiness <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Uneasiness_1_AESTHEMOS_mean, Uneasiness_1_AESTHEMOS_sd,
         Uneasiness_2_AESTHEMOS_mean, Uneasiness_2_AESTHEMOS_sd) %>%
  mutate(Mean_Uneasiness = (`Uneasiness_1_AESTHEMOS_mean` + `Uneasiness_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Uneasiness = sqrt((`Uneasiness_1_AESTHEMOS_sd`^2 + `Uneasiness_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Worried" = Uneasiness_1_AESTHEMOS_mean) %>%
  rename("SD_Worried" = Uneasiness_1_AESTHEMOS_sd) %>%
  rename("Mean_Oppressive" = Uneasiness_2_AESTHEMOS_mean) %>%
  rename("SD_Oppressive" = Uneasiness_2_AESTHEMOS_sd)

Sadness <- ThemesAESTHEMOS_DF_Pivot %>%
  select(Thematic, `Yes/No`,
         Sadness_1_AESTHEMOS_mean, Sadness_1_AESTHEMOS_sd,
         Sadness_2_AESTHEMOS_mean, Sadness_2_AESTHEMOS_sd) %>%
  mutate(Mean_Sadness = (`Sadness_1_AESTHEMOS_mean` + `Sadness_2_AESTHEMOS_mean`)/2) %>%
  mutate(PooledSD_Sadness = sqrt((`Sadness_1_AESTHEMOS_sd`^2 + `Sadness_2_AESTHEMOS_sd`^2)/2)) %>%
  rename("Mean_Sad" = Sadness_1_AESTHEMOS_mean) %>%
  rename("SD_Sad" = Sadness_1_AESTHEMOS_sd) %>%
  rename("Mean_Melancholic" = Sadness_2_AESTHEMOS_mean) %>%
  rename("SD_Melancholic" = Sadness_2_AESTHEMOS_sd)

```

```{r}
Profile_DF <- ThemesAESTHEMOS_DF_Pivot %>%
  #filter(`Yes/No` == 1) %>%
  select(Thematic, `Yes/No`, ends_with("_mean"))
  
Profile_DF_Melted <- melt(Profile_DF, measure.vars = c(3:44))

Profile_DF_Melted$variable <- as.factor(Profile_DF_Melted$variable)

#Reordering AESTHEMOS Dimensions for Graph
Profile_DF_Melted$variable <- fct_relevel(Profile_DF_Melted$variable,
                                          #Negative Emotions
                                          "FeelingOfUgliness_1_AESTHEMOS_mean", "FeelingOfUgliness_2_AESTHEMOS_mean",
                                          "Confusion_1_AESTHEMOS_mean", "Confusion_2_AESTHEMOS_mean",
                                          "Anger_1_AESTHEMOS_mean", "Anger_2_AESTHEMOS_mean",
                                          "Boredom_1_AESTHEMOS_mean", "Boredom_2_AESTHEMOS_mean",
                                          "Uneasiness_1_AESTHEMOS_mean", "Uneasiness_2_AESTHEMOS_mean",
                                          #Prototypical Aesthetic Emotions
                                          "BeingMoved_1_AESTHEMOS_mean", "BeingMoved_2_AESTHEMOS_mean",
                                          "Surprise_1_AESTHEMOS_mean", "Surprise_2_AESTHEMOS_mean",
                                          "Fascination_1_AESTHEMOS_mean", "Fascination_2_AESTHEMOS_mean",
                                          "FeelingOfBeauty_1_AESTHEMOS_mean", "FeelingOfBeauty_2_AESTHEMOS_mean",
                                          "Awe_1_AESTHEMOS_mean", "Awe_2_AESTHEMOS_mean",
                                          #Epistemic Emotions
                                          "IntellectualChallenge_1_AESTHEMOS_mean", "IntellectualChallenge_2_AESTHEMOS_mean",
                                          "Interest_1_AESTHEMOS_mean", "Interest_2_AESTHEMOS_mean",
                                          "Insight_1_AESTHEMOS_mean", "Insight_2_AESTHEMOS_mean",
                                          #Animation
                                          "Energy_1_AESTHEMOS_mean", "Energy_2_AESTHEMOS_mean",
                                          "Vitality_1_AESTHEMOS_mean", "Vitality_2_AESTHEMOS_mean",
                                          "Enchantment_1_AESTHEMOS_mean", "Enchantment_2_AESTHEMOS_mean",
                                          #Nostalgia
                                          "Nostalgia_1_AESTHEMOS_mean", "Nostalgia_2_AESTHEMOS_mean",
                                          "Relaxation_1_AESTHEMOS_mean", "Relaxation_2_AESTHEMOS_mean",
                                          #Sadness
                                          "Sadness_1_AESTHEMOS_mean", "Sadness_2_AESTHEMOS_mean",
                                          #Amusement
                                          "Humor_1_AESTHEMOS_mean", "Humor_2_AESTHEMOS_mean",
                                          "Joy_1_AESTHEMOS_mean", "Joy_2_AESTHEMOS_mean"
                                          )

```


## AESTHEMOS Mean and CIs for each Theme
```{r, fig.width=16, fig.height=10}

ThemesAESTHEMOS_Melted <- ThemesAESTHEMOS_DF_Pivot_Help %>%
  pivot_longer(1:7, names_to = "Thematic", values_to = "Yes/No") %>%
  mutate(`Yes/No`=as.factor(`Yes/No`)) %>%
  mutate(`Thematic`=as.factor(`Thematic`)) %>%
  #This is done manually from the nThemes data frame as fct_recode doesn't work with parse
  mutate(`Thematic` = fct_recode(`Thematic`, "All Games Are Art (9)" = "all games art",
                                 "Craft (66)" = "craft",
                                 "Exploration Of Interpretation (10)" = "exploration of interpretation",
                                 "Expressive Potential of Games (51)" = "Expressive potential of games",
                                 "The Feels (59)" = "The Feels",
                                 "The Thinks (19)" = "the thinks",
                                 "Visual Beauty (37)" = "visual beauty")) %>%
  group_by(`Thematic`, `Yes/No`)




ThemesAESTHEMOS_Melted <- melt(ThemesAESTHEMOS_Melted, id.vars=c(43:44), measure.vars=c(1:42))

ThemesAESTHEMOS_Melted_grp <-ThemesAESTHEMOS_Melted %>%
  filter(`Yes/No`==1) %>%
  group_by(variable, Thematic)

Help <- str_split_fixed(ThemesAESTHEMOS_Melted_grp$Thematic, "\\(", 2)
Help[,2] <- str_sub(Help[,2], end=-2)

ThemesAESTHEMOS_Melted_grp$n <- as.numeric(Help[,2])

ThemesAESTHEMOS_Melted_grp <- ThemesAESTHEMOS_Melted_grp %>%
  group_by(variable, Thematic) %>%
  summarize(Mean=mean(value, na.rm=TRUE), 
            SD=sd(value, na.rm=TRUE), 
            CI=1.96*(sd(value, na.rm=TRUE)*(sqrt((n[1]-1)/n[1])))/sqrt(n[1]),
            Likelihood_Lower = p.interval(na.omit(value))[1],
            Likelihood_Upper = p.interval(na.omit(value))[2]
            )

#Reordering AESTHEMOS Dimensions for Graph
ThemesAESTHEMOS_Melted_grp$variable <- fct_relevel(ThemesAESTHEMOS_Melted_grp$variable,
                                          #Negative Emotions
                                          "FeelingOfUgliness_1_AESTHEMOS", "FeelingOfUgliness_2_AESTHEMOS",
                                          "Confusion_1_AESTHEMOS", "Confusion_2_AESTHEMOS",
                                          "Anger_1_AESTHEMOS", "Anger_2_AESTHEMOS",
                                          "Boredom_1_AESTHEMOS", "Boredom_2_AESTHEMOS",
                                          "Uneasiness_1_AESTHEMOS", "Uneasiness_2_AESTHEMOS",
                                          #Prototypical Aesthetic Emotions
                                          "BeingMoved_1_AESTHEMOS", "BeingMoved_2_AESTHEMOS",
                                          "Surprise_1_AESTHEMOS", "Surprise_2_AESTHEMOS",
                                          "Fascination_1_AESTHEMOS", "Fascination_2_AESTHEMOS",
                                          "FeelingOfBeauty_1_AESTHEMOS", "FeelingOfBeauty_2_AESTHEMOS",
                                          "Awe_1_AESTHEMOS", "Awe_2_AESTHEMOS",
                                          #Epistemic Emotions
                                          "IntellectualChallenge_1_AESTHEMOS", "IntellectualChallenge_2_AESTHEMOS",
                                          "Interest_1_AESTHEMOS", "Interest_2_AESTHEMOS",
                                          "Insight_1_AESTHEMOS", "Insight_2_AESTHEMOS",
                                          #Animation
                                          "Energy_1_AESTHEMOS", "Energy_2_AESTHEMOS",
                                          "Vitality_1_AESTHEMOS", "Vitality_2_AESTHEMOS",
                                          "Enchantment_1_AESTHEMOS", "Enchantment_2_AESTHEMOS",
                                          #Nostalgia
                                          "Nostalgia_1_AESTHEMOS", "Nostalgia_2_AESTHEMOS",
                                          "Relaxation_1_AESTHEMOS", "Relaxation_2_AESTHEMOS",
                                          #Sadness
                                          "Sadness_1_AESTHEMOS", "Sadness_2_AESTHEMOS",
                                          #Amusement
                                          "Humor_1_AESTHEMOS", "Humor_2_AESTHEMOS",
                                          "Joy_1_AESTHEMOS", "Joy_2_AESTHEMOS"
                                          )


ThemesAESTHEMOS_Melted_grp$Thematic <- fct_relevel(ThemesAESTHEMOS_Melted_grp$Thematic,
                                                   "Craft (66)", "The Feels (59)", "Expressive Potential of Games (51)",
                                                   "Visual Beauty (37)", "The Thinks (19)",
                                                   "Exploration Of Interpretation (10)", "All Games Are Art (9)")


ggplot(ThemesAESTHEMOS_Melted_grp, aes(x=variable, y=Mean, color=Thematic)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5))  +
  scale_color_viridis_d(
                      guide = guide_legend(direction = "horizontal", title.position = "top",
                             label.position="bottom", label.hjust = 0.1, label.vjust = 0.5,
                             label.theme = element_text(angle = 90), title=NULL
                             )) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    annotate("rect", xmin=1, xmax=10.25, ymin=1, ymax=5, alpha=.2) +
    annotate("text", x=6, y=5.1,  label="Negative Emotions") +
  annotate("rect", xmin=10.75, xmax=20.25, ymin=1, ymax=5, alpha=.2) +
    annotate("text", x=15.5, y=5.1,  label="Prototypical Aesthetic Emotions") +
  annotate("rect", xmin=20.75, xmax=26.25, ymin=1, ymax=5, alpha=.2) +
    annotate("text", x=23.5, y=5.1,  label="Epistemic Emotions") +
  annotate("rect", xmin=26.75, xmax=32.25, ymin=1, ymax=5, alpha=.2) +
    annotate("text", x=29.5, y=5.1,  label="Animation") +
  annotate("rect", xmin=32.75, xmax=36.25, ymin=1, ymax=5, alpha=.2) +
    annotate("text", x=34.5, y=5.1,  label="Nostalgia/Relaxation") +
  annotate("rect", xmin=36.75, xmax=38.25, ymin=1, ymax=5, alpha=.2) +
    annotate("text", x=37.5, y=5.1,  label="Sadness") +
  annotate("rect", xmin=38.75, xmax=42, ymin=1, ymax=5, alpha=.2) +
    annotate("text", x=40.5, y=5.1,  label="Amusement")

#ggplot(ThemesAESTHEMOS_Melted_grp%>%filter(Thematic=="The Thinks (19)" | Thematic=="Visual Beauty (37)"), aes(x=variable, y=Mean, colour=Thematic)) +
#  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
#  geom_point(position=position_dodge(0.5)) +
#  scale_color_viridis_d(begin=.43, end= .57, guide = guide_legend(direction = "horizontal", title.position = "top",
#                             label.position="bottom", label.hjust = 0.1, label.vjust = 0.5,
#                             label.theme = element_text(angle = 90), title=NULL
#                             )) +
#  theme_minimal()+
#  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#    annotate("rect", xmin=1, xmax=10.25, ymin=1, ymax=5, alpha=.2) +
#    annotate("text", x=6, y=5.1,  label="Negative Emotions") +
#  annotate("rect", xmin=10.75, xmax=20.25, ymin=1, ymax=5, alpha=.2) +
#    annotate("text", x=15.5, y=5.1,  label="Prototypical Aesthetic Emotions") +
#  annotate("rect", xmin=20.75, xmax=26.25, ymin=1, ymax=5, alpha=.2) +
#    annotate("text", x=23.5, y=5.1,  label="Epistemic Emotions") +
#  annotate("rect", xmin=26.75, xmax=32.25, ymin=1, ymax=5, alpha=.2) +
#    annotate("text", x=29.5, y=5.1,  label="Animation") +
#  annotate("rect", xmin=32.75, xmax=36.25, ymin=1, ymax=5, alpha=.2) +
#    annotate("text", x=34.5, y=5.1,  label="Nostalgia/Relaxation") +
#  annotate("rect", xmin=36.75, xmax=38.25, ymin=1, ymax=5, alpha=.2) +
#    annotate("text", x=37.5, y=5.1,  label="Sadness") +
#  annotate("rect", xmin=38.75, xmax=42, ymin=1, ymax=5, alpha=.2) +
#    annotate("text", x=40.5, y=5.1,  label="Amusement")


#ggplot(ThemesAESTHEMOS_Melted_grp%>%filter(Thematic=="The Thinks (19)" | Thematic=="Visual Beauty (37)"), aes(x=variable, y=Mean, colour=Thematic)) +
#  geom_errorbar(aes(ymin=Likelihood_Lower, ymax=Likelihood_Upper), position=position_dodge(0.5)) +
#  geom_point(position=position_dodge(0.5)) +
#  scale_color_viridis_d(begin=.43, end= .57, guide = guide_legend(direction = "horizontal", title.position = "top",
#                             label.position="bottom", label.hjust = 0.1, label.vjust = 0.5,
#                             label.theme = element_text(angle = 90), title=NULL
#                             )) +
#  theme_minimal()+
#  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#    annotate("rect", xmin=1, xmax=10.25, ymin=1, ymax=5, alpha=.2) +
#    annotate("text", x=6, y=5.1,  label="Negative Emotions") +
#  annotate("rect", xmin=10.75, xmax=20.25, ymin=1, ymax=5, alpha=.2) +
#    annotate("text", x=15.5, y=5.1,  label="Prototypical Aesthetic Emotions") +
#  annotate("rect", xmin=20.75, xmax=26.25, ymin=1, ymax=5, alpha=.2) +
#    annotate("text", x=23.5, y=5.1,  label="Epistemic Emotions") +
#  annotate("rect", xmin=26.75, xmax=32.25, ymin=1, ymax=5, alpha=.2) +
#    annotate("text", x=29.5, y=5.1,  label="Animation") +
#  annotate("rect", xmin=32.75, xmax=36.25, ymin=1, ymax=5, alpha=.2) +
#    annotate("text", x=34.5, y=5.1,  label="Nostalgia/Relaxation") +
#  annotate("rect", xmin=36.75, xmax=38.25, ymin=1, ymax=5, alpha=.2) +
#    annotate("text", x=37.5, y=5.1,  label="Sadness") +
#  annotate("rect", xmin=38.75, xmax=42, ymin=1, ymax=5, alpha=.2) +
#    annotate("text", x=40.5, y=5.1,  label="Amusement")

#Cutting up my beloved graph so it fits better in the paper :,(

#Negative Emotions
Melted_NegEmotions <- ThemesAESTHEMOS_Melted_grp %>%
  filter(variable == "FeelingOfUgliness_1_AESTHEMOS" | variable == "FeelingOfUgliness_2_AESTHEMOS"
                                          | variable == "Confusion_1_AESTHEMOS" | variable ==  "Confusion_2_AESTHEMOS"
                                          | variable == "Anger_1_AESTHEMOS" | variable == "Anger_2_AESTHEMOS"
                                          | variable == "Boredom_1_AESTHEMOS" | variable ==  "Boredom_2_AESTHEMOS"
                                          | variable == "Uneasiness_1_AESTHEMOS" | variable ==  "Uneasiness_2_AESTHEMOS")


ggplot(Melted_NegEmotions, aes(x=variable, y=Mean, colour=Thematic)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_color_viridis_d(guide = guide_legend(direction = "horizontal", title.position = "top",
                             label.position="bottom", label.hjust = 0.1, label.vjust = 0.5,
                             label.theme = element_text(angle = 90), title=NULL
                             )) +
  ggtitle("AESTHEMOS Negative Emotions by Theme") +
  theme(axis.text.x = element_text(size=13, face="bold")) +
  xlab(NULL)

#Aesthetic Emotions
Melted_AestheticEmotions <- ThemesAESTHEMOS_Melted_grp %>%
  filter(variable == "BeingMoved_1_AESTHEMOS" | variable== "BeingMoved_2_AESTHEMOS"
                                          | variable== "Surprise_1_AESTHEMOS" | variable==  "Surprise_2_AESTHEMOS"
                                          | variable== "Fascination_1_AESTHEMOS" | variable==  "Fascination_2_AESTHEMOS"
                                          | variable== "FeelingOfBeauty_1_AESTHEMOS" | variable==  "FeelingOfBeauty_2_AESTHEMOS"
                                          | variable== "Awe_1_AESTHEMOS" | variable==  "Awe_2_AESTHEMOS")


ggplot(Melted_AestheticEmotions, aes(x=variable, y=Mean, colour=Thematic)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_color_viridis_d(guide = guide_legend(direction = "horizontal", title.position = "top",
                             label.position="bottom", label.hjust = 0.1, label.vjust = 0.5,
                             label.theme = element_text(angle = 90), title=NULL
                             )) +
  ggtitle("AESTHEMOS Prototypical Aesthetic Emotions by Theme") +
  theme(axis.text.x = element_text(size=15, face="bold")) +
  xlab(NULL)


#Epistemic Emotions
Melted_EpistemicEmotions <- ThemesAESTHEMOS_Melted_grp %>%
  filter(variable == "IntellectualChallenge_1_AESTHEMOS" | variable ==  "IntellectualChallenge_2_AESTHEMOS"
                                          | variable ==  "Interest_1_AESTHEMOS" | variable ==   "Interest_2_AESTHEMOS"
                                          | variable ==  "Insight_1_AESTHEMOS" | variable ==   "Insight_2_AESTHEMOS")


ggplot(Melted_EpistemicEmotions, aes(x=variable, y=Mean, colour=Thematic)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_color_viridis_d(guide = guide_legend(direction = "horizontal", title.position = "top",
                             label.position="bottom", label.hjust = 0.1, label.vjust = 0.5,
                             label.theme = element_text(angle = 90), title=NULL
                             )) +
  ggtitle("AESTHEMOS Epistemic Emotions by Theme") +
  theme(axis.text.x = element_text(size=15, face="bold")) +
  xlab(NULL)

#Animation
Melted_Animation <- ThemesAESTHEMOS_Melted_grp %>%
  filter(variable == "Energy_1_AESTHEMOS" | variable ==   "Energy_2_AESTHEMOS"
                                          | variable ==  "Vitality_1_AESTHEMOS" | variable ==   "Vitality_2_AESTHEMOS"
                                          | variable ==  "Enchantment_1_AESTHEMOS" | variable ==   "Enchantment_2_AESTHEMOS")


ggplot(Melted_Animation, aes(x=variable, y=Mean, colour=Thematic)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_color_viridis_d(guide = guide_legend(direction = "horizontal", title.position = "top",
                             label.position="bottom", label.hjust = 0.1, label.vjust = 0.5,
                             label.theme = element_text(angle = 90), title=NULL
                             )) +
  ggtitle("AESTHEMOS Animation by Theme") +
  theme(axis.text.x = element_text(size=15, face="bold")) +
  xlab(NULL)

#Nostalgia, Sadness and Amuesement
Melted_Nostalgia <- ThemesAESTHEMOS_Melted_grp %>%
  filter(variable ==  "Nostalgia_1_AESTHEMOS" | variable == "Nostalgia_2_AESTHEMOS"
                                           | variable == "Relaxation_1_AESTHEMOS" | variable ==  "Relaxation_2_AESTHEMOS"
                                          #Sadness
                                           | variable == "Sadness_1_AESTHEMOS" | variable ==  "Sadness_2_AESTHEMOS"
                                          #Amusement
                                           | variable == "Humor_1_AESTHEMOS" | variable ==  "Humor_2_AESTHEMOS"
                                           | variable == "Joy_1_AESTHEMOS" | variable ==  "Joy_2_AESTHEMOS")


ggplot(Melted_Nostalgia, aes(x=variable, y=Mean, colour=Thematic)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_color_viridis_d(guide = guide_legend(direction = "horizontal", title.position = "top",
                             label.position="bottom", label.hjust = 0.1, label.vjust = 0.5,
                             label.theme = element_text(angle = 90), title=NULL
                             )) +
  ggtitle("AESTHEMOS Nostalgia/Relaxation, Sadness, and Amusement by Theme") +
    annotate("rect", xmin=0.70, xmax=4.35, ymin=1, ymax=5, alpha=.2) +
    annotate("text", x=2.5, y=5.1,  label="Nostalgia/Relaxation", size=8) +
  annotate("rect", xmin=4.65, xmax=6.35, ymin=1, ymax=5, alpha=.2) +
    annotate("text", x=5.5, y=5.1,  label="Sadness", size=8) +
  annotate("rect", xmin=6.65, xmax=10.25, ymin=1, ymax=5, alpha=.2) +
    annotate("text", x=8.5, y=5.1,  label="Amusement", size=8) +
  theme(axis.text.x = element_text(size=15, face="bold")) +
  xlab(NULL)
```



## Each AESTHEMOS item per Theme
```{r}
#FeelingOfUgliness
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="FeelingOfUgliness_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("FeelingOfUgliness_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="FeelingOfUgliness_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("FeelingOfUgliness_2") +
  ylim(min=1, max=5)

#Confusion
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Confusion_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Confusion_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Confusion_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Confusion_2") +
  ylim(min=1, max=5)

#Anger
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Anger_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Anger_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Anger_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Anger_2") +
  ylim(min=1, max=5)

#Boredom
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Boredom_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Boredom_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Boredom_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Boredom_2") +
  ylim(min=1, max=5)

#Uneasiness
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Uneasiness_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Uneasiness_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Uneasiness_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Uneasiness_2") +
  ylim(min=1, max=5)

#BeingMoved
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="BeingMoved_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("BeingMoved_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="BeingMoved_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("BeingMoved_2") +
  ylim(min=1, max=5)

#Surprise
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Surprise_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Surprise_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Surprise_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Surprise_2") +
  ylim(min=1, max=5)

#Fascination
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Fascination_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Fascination_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Fascination_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Fascination_2") +
  ylim(min=1, max=5)

#FeelingOfBeauty
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="FeelingOfBeauty_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("FeelingOfBeauty_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="FeelingOfBeauty_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("FeelingOfBeauty_2") +
  ylim(min=1, max=5)

#Awe
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Awe_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Awe_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Awe_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Awe_2") +
  ylim(min=1, max=5)

#IntellectualChallenge
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="IntellectualChallenge_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("IntellectualChallenge_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="IntellectualChallenge_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("IntellectualChallenge_2") +
  ylim(min=1, max=5)

#Interest
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Interest_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Interest_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Interest_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Interest_2") +
  ylim(min=1, max=5)

#Insight
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Insight_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Insight_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Insight_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Insight_2") +
  ylim(min=1, max=5)

#Energy
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Energy_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Energy_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Energy_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Energy_2") +
  ylim(min=1, max=5)

#Vitality
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Vitality_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Vitality_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Vitality_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Vitality_2") +
  ylim(min=1, max=5)

#Enchantment
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Enchantment_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Enchantment_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Enchantment_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Enchantment_2") +
  ylim(min=1, max=5)

#Nostalgia
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Nostalgia_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Nostalgia_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Nostalgia_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Nostalgia_2") +
  ylim(min=1, max=5)

#Relaxation
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Relaxation_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Relaxation_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Relaxation_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Relaxation_2") +
  ylim(min=1, max=5)

#Sadness
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Sadness_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Sadness_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Sadness_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Sadness_2") +
  ylim(min=1, max=5)

#Humor
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Humor_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Humor_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Humor_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Humor_2") +
  ylim(min=1, max=5)

#Joy
ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Joy_1_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Joy_1") +
  ylim(min=1, max=5)

ggplot(ThemesAESTHEMOS_Melted_grp %>% filter(variable=="Joy_2_AESTHEMOS"), aes(x=Thematic, y=Mean)) +
  geom_errorbar(aes(ymin=ifelse(Mean-CI<=1, 1, Mean-CI), ymax=ifelse(Mean+CI>5, 5, Mean+CI)), position=position_dodge(0.5)) +
  geom_point(position=position_dodge(0.5)) +
  ylab("Joy_2") +
  ylim(min=1, max=5)
```

